### 2025-03-07 paper/sections/other/grids.qmd
some notes from meeting and updates to appendix

@@

```{julia}
#| output: asis
dict = CTExperiments.from_toml(joinpath(res_dir,"gen_params/mlp/lin_sep/grid_config.toml")) 
println(CTExperiments.dict_to_quarto_markdown(dict))
```

@@

```{julia}
#| output: asis
dict = CTExperiments.from_toml(joinpath(res_dir, "gen_params/mlp/lin_sep/evaluation/evaluation_grid_config.toml"))
println(CTExperiments.dict_to_quarto_markdown(dict))
```

@@

### High-Level Findings

![](/paper/experiments/output/final_run/gen_params/mlp/moons/evaluation/results/ce/decision_threshold_exper---lambda_energy_exper---maxiter_exper---maxiter---decision_threshold_exper/plausibility_distance_from_target.png)

![](/paper/experiments/output/final_run/gen_params/mlp/moons/evaluation/results/ce/decision_threshold_exper---lambda_energy_exper---maxiter_exper---maxiter---decision_threshold_exper/distance.png)

![](/paper/experiments/output/final_run/gen_params/mlp/moons/evaluation/results/logs/objective---lambda_energy---generator_type---maxiter/percent_valid.png)

![](/paper/experiments/output/final_run/gen_params/mlp/moons/evaluation/results/logs/objective---lambda_energy---generator_type---maxiter/acc_val.png)

### Detailed Findings

```{julia}
gen_params_dir = joinpath(res_dir, "gen_params/mlp")
```

#### Linearly Separable

```{julia}
df = CSV.read("$(gen_params_dir)/lin_sep/evaluation/results/ce/decision_threshold_exper---lambda_energy_exper---maxiter_exper---maxiter---decision_threshold_exper/plausibility_distance_from_target.csv", DataFrame)
select!(df, Not(:objective))
df = groupby(df, Not(:run, :mean, :lambda_energy_eval, :is_pct)) |> 
  gdf -> combine(gdf, :mean => (x -> [(mean(x),std(x))]) => [:value,:std]) |>
  df -> sort(df, [:lambda_energy_exper, :decision_threshold_exper, :maxiter_exper, :generator_type])
```

::: {#tbl-lin_sep-lambda_energy_exper}

::: {.content-hidden unless-format="pdf"}

@@

using CTExperiments.ColorSchemes
get_table_inputs(df, "value"; alpha=0.9, byvars=["lambda_energy_exper", "decision_threshold_exper", "maxiter_exper"], backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; wrap_table=false)
```

@@

Results for Linearly Separable data by energy penalty.

@@

>>>>

```{julia}
grid_dir = joinpath(res_dir, "gen_params/mlp")
data_dirs = readdir(grid_dir) |> x -> joinpath.(grid_dir, x) |> x -> x[isdir.(x)]
data_names = basename.(data_dirs)
suffix = "evaluation/results/ce/decision_threshold_exper---lambda_energy_exper---maxiter_exper---maxiter---decision_threshold_exper/"
```

@@

```{julia}
#| output: asis
dict = CTExperiments.from_toml(joinpath(grid_dir, "lin_sep/grid_config.toml")) 
println(CTExperiments.dict_to_quarto_markdown(dict))
```

@@

```{julia}
#| output: asis
dict = CTExperiments.from_toml(joinpath(grid_dir, "lin_sep/evaluation/evaluation_grid_config.toml"))
println(CTExperiments.dict_to_quarto_markdown(dict))
```

@@

#### Plausibility

@@

fig_label_prefix = "grid-gen_params-plaus"
fig_labels = (nm -> "fig-$(fig_label_prefix)-$nm").(data_names)
_str = "The results with respect to the plausibility measure are shown in @$(fig_labels[1]) to @$(fig_labels[end])."
println(_str)
```

imgfname = "plausibility_distance_from_target.png"
fig_caption = "Average outcomes for the plausibility measure across hyperparameters."
full_paths = joinpath.(data_dirs, joinpath(suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption) 
_str = join(include_img_commands, "\n\n")
println(_str)
```

#### Cost

fig_label_prefix = "grid-gen_params-cost"
fig_labels = (nm -> "fig-$(fig_label_prefix)-$nm").(data_names)
_str = "The results with respect to the cost measure are shown in @$(fig_labels[1]) to @$(fig_labels[end])."
println(_str)
```

imgfname = "distance.png"
fig_caption = "Average outcomes for the cost measure across hyperparameters."
full_paths = joinpath.(data_dirs, joinpath(suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption)
_str = join(include_img_commands, "\n\n")
println(_str)
```

### Penalty Strengths

```{julia}
grid_dir = joinpath(res_dir, "penalties/mlp")
data_dirs = readdir(grid_dir) |> x -> joinpath.(grid_dir, x) |> x -> x[isdir.(x)]
data_names = basename.(data_dirs)
suffix = "evaluation/results/ce/lambda_adversarial---lambda_energy_reg---lambda_energy_diff---lambda_adversarial---lambda_adversarial/"
```

The hyperparameter grid with varying penalty strengths during training is shown in @nte-pen-final-run-train. The corresponding evaluation grid used for these experiments is shown in @nte-pen-final-run-eval.

::: {#nte-pen-final-run-train .callout-note}

```{julia}
#| output: asis
dict = CTExperiments.from_toml(joinpath(grid_dir, "lin_sep/grid_config.toml")) 
println(CTExperiments.dict_to_quarto_markdown(dict))
```

@@

::: {#nte-pen-final-run-eval .callout-note}

```{julia}
#| output: asis
dict = CTExperiments.from_toml(joinpath(grid_dir, "lin_sep/evaluation/evaluation_grid_config.toml"))
println(CTExperiments.dict_to_quarto_markdown(dict))
```

@@

#### Plausibility

fig_label_prefix = "grid-pen-plaus"
fig_labels = (nm -> "fig-$(fig_label_prefix)-$nm").(data_names)
_str = "The results with respect to the plausibility measure are shown in @$(fig_labels[1]) to @$(fig_labels[end])."
println(_str)
```

imgfname = "plausibility_distance_from_target.png"
fig_caption = "Average outcomes for the plausibility measure across hyperparameters."
full_paths = joinpath.(data_dirs, joinpath(suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption) 
_str = join(include_img_commands, "\n\n")
println(_str)
```

#### Cost

fig_label_prefix = "grid-pen-cost"
fig_labels = (nm -> "fig-$(fig_label_prefix)-$nm").(data_names)
_str = "The results with respect to the cost measure are shown in @$(fig_labels[1]) to @$(fig_labels[end])."
println(_str)
```

imgfname = "distance.png"
fig_caption = "Average outcomes for the cost measure across hyperparameters."
full_paths = joinpath.(data_dirs, joinpath(suffix,imgfname))
include_img_commands = CTExperiments.get_img_command(data_names, full_paths, fig_labels; fig_caption)
_str = join(include_img_commands, "\n\n")
println(_str)
```
